\bf Model Visualization Techniques for a Social Network Model

### 2018-07-25 paper-child.Rnw
trying to comply with ASA guidelines

% table of fitted M1 M2 M3
\begin{table}
\scalebox{0.9}{
\begin{tabular}{l|ccc|ccc }
  \hline
  & \multicolumn{3}{|c|}{Friendship Data} & \multicolumn{3}{|c|}{Senate Data} \\
  \hline
  & M1 & M2 & M3 & M1 & M2 & M3 \\
  $\alpha_1$ & \Sexpr{SFE$M1[1]} & \Sexpr{SFE$M2[1]} & \Sexpr{SFE$M3[1]} & \Sexpr{SSE$M1[1]} & \Sexpr{SSE$M2[1]} & \Sexpr{SSE$M3[1]} \\
  $\alpha_2$ & \Sexpr{SFE$M1[2]} & \Sexpr{SFE$M2[2]} & \Sexpr{SFE$M3[2]} & \Sexpr{SSE$M1[2]} & \Sexpr{SSE$M2[2]} & \Sexpr{SSE$M3[2]}  \\
  $\alpha_3$ & -- & -- & -- & \Sexpr{SSE$M1[3]} & \Sexpr{SSE$M2[3]} & \Sexpr{SSE$M3[3]} \\
  $\beta_1$ & \Sexpr{SFE$M1[3]} & \Sexpr{SFE$M2[3]} & \Sexpr{SFE$M3[3]} & \Sexpr{SSE$M1[4]} & \Sexpr{SSE$M2[4]} & \Sexpr{SSE$M3[4]} \\
  $\beta_2$ & \Sexpr{SFE$M1[4]} & \Sexpr{SFE$M2[4]} & \Sexpr{SFE$M3[4]} & \Sexpr{SSE$M1[5]} & \Sexpr{SSE$M2[5]} & \Sexpr{SSE$M3[5]}\\
$\beta_3$ & -- & \Sexpr{SFE$M2[5]} & -- & -- & \Sexpr{SSE$M2[6]} & -- \\
  $\beta_4$ & -- & --  & \Sexpr{SFE$M3[6]} & -- & -- & \Sexpr{SSE$M3[7]} \\
  \hline
\end{tabular}
}
\caption{\label{tab:meanests} The means (std. dev.) of parameter values estimated from repeated fittings of $M1, M2, M3$ to the two example data sets.}
\end{table}

>>>>

% table of fitted M1 M2 M3
\begin{table}
\scalebox{0.9}{
\begin{tabular}{lcccccc }

  & \multicolumn{3}{|c|}{Friendship Data} & \multicolumn{3}{|c|}{Senate Data} \\
  \hline
  & M1 & M2 & M3 & M1 & M2 & M3 \\
  \hline
  $\alpha_1$ & \Sexpr{SFE$M1[1]} & \Sexpr{SFE$M2[1]} & \Sexpr{SFE$M3[1]} & \Sexpr{SSE$M1[1]} & \Sexpr{SSE$M2[1]} & \Sexpr{SSE$M3[1]} \\
  $\alpha_2$ & \Sexpr{SFE$M1[2]} & \Sexpr{SFE$M2[2]} & \Sexpr{SFE$M3[2]} & \Sexpr{SSE$M1[2]} & \Sexpr{SSE$M2[2]} & \Sexpr{SSE$M3[2]}  \\
  $\alpha_3$ & -- & -- & -- & \Sexpr{SSE$M1[3]} & \Sexpr{SSE$M2[3]} & \Sexpr{SSE$M3[3]} \\
  \hline
  $\beta_1$ & \Sexpr{SFE$M1[3]} & \Sexpr{SFE$M2[3]} & \Sexpr{SFE$M3[3]} & \Sexpr{SSE$M1[4]} & \Sexpr{SSE$M2[4]} & \Sexpr{SSE$M3[4]} \\
  $\beta_2$ & \Sexpr{SFE$M1[4]} & \Sexpr{SFE$M2[4]} & \Sexpr{SFE$M3[4]} & \Sexpr{SSE$M1[5]} & \Sexpr{SSE$M2[5]} & \Sexpr{SSE$M3[5]}\\
$\beta_3$ & -- & \Sexpr{SFE$M2[5]} & -- & -- & \Sexpr{SSE$M2[6]} & -- \\
  $\beta_4$ & -- & --  & \Sexpr{SFE$M3[6]} & -- & -- & \Sexpr{SSE$M3[7]} \\
  \hline
\end{tabular}
}
\caption{\label{tab:meanests} The means (std. dev.) of parameter values estimated from repeated fittings of $M1, M2, M3$ to the two example data sets.}
\end{table}
